---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HMISprep

<!-- badges: start -->
<!-- badges: end -->

`HMISprep` processes and cleans Homeless Management Information System (HMIS) 
data for reporting and analysis. Provides functions to validate, transform, 
and prepare HMIS datasets according to HUD reporting specifications. Designed 
as part of a data pipeline that feeds 'HMISserve' backend reporting and 
Shiny applications, enabling standardized data quality checks and automated 
reporting workflows.

## Installation

You can install the development version of HMISprep from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("COHHIO/HMISprep")
```

## Prerequisites

This package requires AWS credentials to access S3 buckets. You can configure credentials using one of these methods:

1. **AWS credentials file** (`~/.aws/credentials`)
2. **Environment variables** (`AWS_ACCESS_KEY_ID`, `AWS_SECRET_ACCESS_KEY`)

See the [aws.s3 package documentation](https://github.com/cloudyr/aws.s3) for more details on authentication.

## Usage

### Cleaning HMIS CSV Files
```{r, eval=FALSE}
library(HMISdata)

# Prep Enrollment dataframe
prep_enrollment()
```
